---
title: "Session 2B"
author: "Halina Do-Linh"
date: "8/3/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

#### *Palmer Penguins was developed by Allison with two researchers from University of Alaska to replace the racist burdened irises dataset that was often used by data science professors.*

## Plot a function in `ggplot2`

#### *use back ticks \`\` to notate code. As seen above for ggplot2.*

```{r}
eq <- function(x) {
  
  3 * x ^ 2 + 4
  
}

# Use stat_function()
# ggplot is particular and expects a data frame and not vectors
# We are specifying end points in a data frame using c()

ggplot(data = data.frame(x = c(1, 100)), aes(x = x)) +
  stat_function(fun = eq)


```

### Task

*Use dollar signs for LATEX (LAH-tech). This is to have nice looking equations in my document.*

Plot $f(x)=2.4-5x^3+2.1*x^2$

Over a range of -50 to 50.

```{r}

eq <- function(x) {
  
  2.4 - 5 * (x ^ 3) + 2.1 * (x ^ 2)
  
}

ggplot(data = data.frame(x = c(-50, 50)), aes(x = x)) + 
         stat_function(fun = eq)



```

### `penguins` body mass and flipper lengths

Basic ggplot scatter plot of body mass (y) and flipper length (x)

```{r}

# ggplot needs three pieces of information to make a basic graph: Where is the data coming from? What variables are you using aka what is your x and y? What kind of graph (i.e. geom_point)?
# use cmd + shift + C to comment out or comment in lines of code
# anytime you want to update ggplot with a variable use aes()
# anytime you want to update ggplot with NOT a variable include it outside aes()
# ggplot cheat sheet, cookbook and more online for graph customization
# you can use color codes to specify colors as well. There are entire color palettes online!
# colors are assigned in the order that R recognizes the groups and groups tend to be organized alphabetically
# look up what facet wrap does...

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) + 
  scale_color_manual(values = c("red", "purple", "blue")) + 
  labs(x = "Flipper Length (mm)", 
       y = "Body Mass (g)", 
       title = "Palmer Penguins Size Measurements", 
       caption = "Data collected by KB Gorman et al. at Palmer Station",
       color = "Species") +
  facet_wrap(~island) +
  theme_light()

```

Describing the graph:

-   There is a positive correlation.

-   There is a linear relationship.

-   Hetero-spaticity or homo-spacticity aka the range of the model is well represented.

-   There are a few clusters of data.

-   *What are the trends? What are the limits?* *Important to look at axis*


### Higher Order Derivative
```{r}
gt <- expression(2.2 + 3.1 * t - 5.6 * t ^ 4)

dg_dt <- D(expr = gt, "t")

dg_dt

```

```{r}

d2g_gt2 <- D(expr = dg_dt, "t")

d2g_gt2

```

### Partial Derivatives
```{r}

f_xyz <- expression(2 * x * y - 3 * (x ^ 2) * (z ^ 3))

df_dx <- D(expr = f_xyz, "x")

df_dy <- D(expr = f_xyz, "y")

df_dz <- D(expr = f_xyz, "z")

```

